### 2014-05-30 article_review.tex
gf

% Table generated by Excel2LaTeX from sheet 'Лист2'
\begin{table}[htbp]
  \centering
  \caption{Операционные характеристики ПЭТ}
    \begin{tabular}{rrr}
          & Чувствительность & Специфичность \\ \hline
    Wang и др. 2013 \cite{wang_fdg-pet_2013} & 91\% (88\%-93\%) & 81\% (75\%-85\%) \\ \hline
    Rijkers и др., 2014\cite{rijkers_usefulness_2014} & 90\% (86\%-93\%) & 76\% (69\%-82\%) \\ \hline
    Tang и др., 2011\cite{tang_usefulness_2011} & 88\% (86\%-90\%) & 88\% (86\%-90\%) \\ \hline
    Orlando и др., 2004 \cite{orlando_meta-analysis:_2004} & 81\% (72\%-88\%) & 66\% ( 53\%-77\%) \\ \hline
    Wu и др., 2012\cite{wu_diagnostic_2012} (PET/CT) & 87\% (82\%-91\%) & 83\% (71\%-91\%) \\ \hline
    \end{tabular}%
  \label{tab:pet_metas}%
\end{table}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Лист2'
\begin{table}[htbp]
  \centering
  \caption{Операционные характеристики ПЭТ}
    \begin{tabular}{rrr}
          & Чувствительность & Специфичность \\ \hline
    Wang и др. 2013 \cite{wang_fdg-pet_2013} & 91 (88-93) & 81 (75-85) \\ \hline
    Rijkers и др., 2014\cite{rijkers_usefulness_2014} & 90 (86-93) & 76 (69-82) \\ \hline
    Tang и др., 2011\cite{tang_usefulness_2011} & 88 (86-90) & 88 (86-90) \\ \hline
    Orlando и др., 2004 \cite{orlando_meta-analysis:_2004} & 81 (72-88) & 66 ( 53-77) \\ \hline
    Wu и др., 2012\cite{wu_diagnostic_2012} (PET/CT) & 87 (82-91) & 83 (71-91) \\ \hline
    \end{tabular}%
  \label{tab:pet_metas}%
\end{table}%
